Security Audit of Safeplug

### 2014-01-09 bibliography.tex
Marvell SoC link
added photos and bibitem

>>>>

\bibitem{marvellhw} Marvell, ``88F6190 and 88F6192 Integrated Controller Hardware Specifications'' 2 December 2008. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/HW_88F619x_OpenSource.pdf}

\bibitem{marvell} Marvell, ``Marvell 88F6192 SoC with Sheeva Technology'' 2009. \url{http://www.marvell.com//embedded-processors/kirkwood/assets/88F6192-003_ver1.pdf}

\bibitem{marvell2} Marvell, ``Marvell Alaska 88E1116R'' 2007. \url{http://www.marvell.com/transceivers/assets/Marvell-Alaska-88E1116R-Single-Port-GbE.pdf}
